### 2017-05-22 sheets/basis-2/sheet-basis-2.tex
Fixed my solutions.

\begin{answer}
  Define
  \begin{align*}
    i(a)&=a &(a\in A)
  \end{align*}
  and
  \begin{align*}
    f(\epsilon)&=0_M&\\
    f(a_1\cdots a_{n-1}a_n)&=f(a_1\cdots a_{n-1})\of j(a_n) &\text{for }n>0.
  \end{align*}
  Clearly, for each $a\in A$, $f(i(a))=j(a)$, thus $f\of i=j$, and $f$ is a group homomorphism.

  Now, suppose $g$ is a group homomorphism satisfying $g\of i=j$.
  Let $a_1\cdots a_n\in A^*$. Proof by induction on $n$ that $g(a_1\cdots a_n)=f(a_1\cdots a_n)$.

@@

  Inductive step:
  \begin{align*}
    g(a_1\cdots a_{n-1}a_n)&=g(a_1\cdots a_{n-1})\of g(a_n)&g\text{ group homomorphism}\\
                           &=f(a_1\cdots a_{n-1})\of g(a_n)&\text{inductive hypothesis}\\
                           &=f(a_1\cdots a_{n-1})\of g(i(a_n)) & a_n\in A\\
                           &=f(a_1\cdots a_{n-1})\of f(i(a_n)) & g\of i=j=f\of i\\
                           &=f(a_1\cdots a_{n-1})\of f(a_n) & a_n\in A\\
                           &=f(a_1\cdots a_{n-1}a_n)&f\text{ group homomorphism}
  \end{align*}
  Hence, $f=g$, so $f$ is indeed unique.

@@

    Indeed, the reverse is also true: Given any injection $f'\from A'\to B'$ there is functor $F\from \A\to\Set$ such that $f'$ corresponds to $F$ (in the way specified above).
  \end{enumerate}
\end{answer}

>>>>

\begin{answer}
  Define
  \begin{align*}
    i(a)&=a &(a\in A)
  \end{align*}
  and
  \begin{align*}
    f(\epsilon)&=0_M&\\
    f(a_1\cdots a_{n-1}a_n)&=f(a_1\cdots a_{n-1})\of j(a_n) &\text{for }n>0.
  \end{align*}
  Clearly, for each $a\in A$, $f(i(a))=j(a)$, thus $f\of i=j$, and $f$ is a monoid homomorphism.

  Now, suppose $g$ is a monoid homomorphism satisfying $g\of i=j$.
  Let $a_1\cdots a_n\in A^*$. Proof by induction on $n$ that $g(a_1\cdots a_n)=f(a_1\cdots a_n)$.

@@

  Inductive step:
  \begin{align*}
    g(a_1\cdots a_{n-1}a_n)&=g(a_1\cdots a_{n-1})\of g(a_n)&g\text{ monoid homomorphism}\\
                           &=f(a_1\cdots a_{n-1})\of g(a_n)&\text{inductive hypothesis}\\
                           &=f(a_1\cdots a_{n-1})\of g(i(a_n)) & a_n\in A\\
                           &=f(a_1\cdots a_{n-1})\of f(i(a_n)) & g\of i=j=f\of i\\
                           &=f(a_1\cdots a_{n-1})\of f(a_n) & a_n\in A\\
                           &=f(a_1\cdots a_{n-1}a_n)&f\text{ monoid homomorphism}
  \end{align*}
  Hence, $f=g$, so $f$ is indeed unique.

@@

    Indeed, assuming the axiom of choice the reverse is also true: Given any injection $f'\from A'\to B'$ there is functor $F\from \A\to\Set$ such that $f'$ corresponds to $F$ (in the way specified above). ($g$ is mapped to the left inverse of $f$, which can be constructed by picking for any $b'$ in the image of $f'$ an arbitrary preimage of $b'$ under $f'$ (axiom of choice!) and for any $b'$ not in the image of $f'$ an arbitrary element of $A'$ (again axiom of choice!)).
  \end{enumerate}
\end{answer}
